Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/theory_results.tex
Discussion of results now written. Still need to explain plots.
prepping for merge

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{bolt}}$ and $\ep_{\text{mult}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
\end{equation}

\end{thm}

@@

% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.

>>>>

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\ep_{Q^*}$, $\ep_{\text{model}}$, $\ep_{\text{mult}}$ and $\ep_{\text{bolt}}$ for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\epsilon$:
\begin{equation}
\forall_{s \in \mathcal{S}_G}: | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq poly(\epsilon).
\end{equation}
\end{thm}

@@

% zzz I don't understand what ``the'' Q function means. if it's the optimal values, we already had a notation for these and I don't see why there should be another.
% "The" q function is the optimal one.
